### 2015-03-02 fundamentals/impl.tex
addresses the concern that agents were not defined clearly before that vocabulary began to be used. The comment was 'readers may be confused by the meaning of 'agent' and 'process' in connection with the NFC and Cyclus.  Would it be possible to offer concise definitions?'

The architecture of \Cyclus allows developers to define nuclear fuel cycle
agents and processes independent of the simulation logic. To achieve this,
agents are developed using the \Cyclus framework \gls{API}, a set of functions
and protocols which assist in agent development and specify how agents should be
defined.  This encapsulated `plug-in' design choice provides two major
benefits. First, analysts can take advantage of the
simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to
their specific problem.  A modeler can focus on creating or customizing
nuclear facility, institution, resource, and toolkit models within their
specific area of technical expertise. Second, because \Cyclus uses a modular
archetype approach, comparing two archetypes is straightforward. For example, if
an analyst would like to compare the effect of using different models to
determine the input fuel composition for fast reactors, fuel
fabrication archetypes can be developed and interchanged while keeping the rest
of the models used in the simulation fixed.

>>>>

The architecture of \Cyclus allows developers to define nuclear fuel cycle
processes independent of the simulation logic. To achieve this, agents are
developed to represent facilities, institutions, and regions comprising the
nuclear fuel cycle. These agents are created using the \Cyclus framework
\gls{API}, a set of functions and protocols which assist in agent development
and specify how agents should be defined.  This encapsulated `plug-in' design
choice provides two major benefits. First, analysts can take advantage of the
simulation logic \gls{API} and archetype ecosystem when they apply \Cyclus to
their specific problem.  A modeler can focus on creating or customizing
nuclear facility, institution, resource, and toolkit models within their
specific area of technical expertise. Second, because \Cyclus uses a modular
archetype approach, comparing two archetypes is straightforward. For example, if
an analyst would like to compare the effect of using different models to
determine the input fuel composition for fast reactors, fuel
fabrication archetypes can be developed and interchanged while keeping the rest
of the models used in the simulation fixed.
